Using reference models in variable selection \vspace{.1in}

### 2020-04-24 paper/ref_approach.tex
improve table 2

\begin{table}[tp]
\footnotesize
\centering
\begin{tabular}{ll|rrrr}
%  \hline
Data  & Method & RMSE Full & RMSE Selected & \# Selected (avg, sd) & \# Selected noisy \\ 
  \hline
bodyfat & projpred & 4.36 & 4.45 & 2 (2.3, 0.48) &   \\
& steplm & 4.38 & 4.46 & 7 (6, 0.94) &  \\
\hline
+ noisy variables & projpred & 4.58 & 4.54 & 2 (2, 0)& 0  \\
& steplm & 5.89 & 5.43 & 23 (26.2, 4.54) & 15 \\
%   \hline
\end{tabular}
\caption{Predictive performances with original bodyfat data (first two
  rows) and with extra noisy variables (last two rows) estimated with
  10-fold cross-validation. Abbreviations: Full = full model; Selected =
  selected submodel; \# Selected = selected number of variables;
  \# Selected noisy = selected number of extra noisy variables. 
  Between brackets average number of selected features and one standard deviation
  values over the 10-fold cross-validation.}
\label{tab:model_performances}
\end{table}

>>>>

\begin{table}[tp]
\footnotesize
\centering
\begin{tabular}{ll|rrrr}
%  \hline
Data  & Method & RMSE Full & RMSE Sel & \# Sel (CPL, AVG, SD) & \# Sel noisy (CPL, AVG, SD) \\ 
  \hline
bodyfat & projpred & 4.36 & 4.45 & (2, 2.3, 0.48) &   \\
& steplm & 4.38 & 4.46 & (7, 6, 0.94) &  \\
\hline
+ noisy variables & projpred & 4.58 & 4.54 & (2, 2, 0)& 0  \\
& steplm & 5.89 & 5.43 & (23, 26.2, 4.54) & 15 \\
%   \hline
\end{tabular}
\caption{Predictive performances with original bodyfat data (first two
  rows) and with extra noisy variables (last two rows) estimated with
  10-fold cross-validation. Abbreviations: RMSE = root mean squared error;
  Full = full model; Sel = selected submodel; 
  \# Sel = total number of selected variables;
  \# Sel noisy = number of selected noisy variables. 
  CPL = results for the complete data (not using cross-validation).
  AVG = average over the 10-fold cross-validation. SD = standard deviation
  over the 10-fold cross-validation.}
\label{tab:model_performances}
\end{table}
